Generating the Blueprints of the Java Ecosystem

### 2015-02-27 msr.tex
fixed scale on database schema figure
almost there

\begin{figure*}
\centering
\includegraphics[scale=0.5]{database-schema}
\caption{The database schema}
\label{fig:database-schema}
\end{figure*}

@@

This dataset followed a narrow selection process, identifying and analysing only projects that were written in Java and had the source code and the binary {\sc jar} available in the repository. The latter reduced significantly the number of projects that were analysed, since many of them provided only the binary {\sc jar}. Since only \textit{clmt} analyses the source code, this ended in drastically reduction of measurements that were exposing object-oriented and package design issues.

>>>>

\begin{figure*}
\centering
\includegraphics[scale=0.7]{database-schema}
\caption{The database schema}
\label{fig:database-schema}
\end{figure*}

@@

This dataset adopted a narrow selection process, identifying and analysing only projects that were written in Java and had both the source code and the binary {\sc jar} available in the repository. The latter reduced significantly the number of projects that were analysed, since many of them provided only the binary {\sc jar}. Since only \textit{clmt} analyses the source code, this ended in drastically reduction of measurements that were exposing object-oriented and package design issues.
